---
title: 'Parse WorkFlowy Journal'
author: "kyle wurtz"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: true
    theme: yeti
    code_folding: show
---

## Setup
### Load Packages
```{r load packages, warning = FALSE, message = FALSE}
require(tidyverse)
require(magrittr)
require(xml2)
require(stringr)
require(lubridate)
```

### Set Up Root Folder
```{r setup, include=FALSE}
require(knitr)
require(rprojroot)
opts_knit$set(root.dir = rprojroot::find_root("WorkFlowy Journal.Rproj"))
```

### Read Day Data
```{r read in sample day data, eval = FALSE}
# read in data in opml format
day = read_xml("Data/Input/day.txt")
day = xml_children(day)[2] # get rid of head
day = xml_child(day, 1) # get XML node

# get string for date
date = xml_attr(day, "text")

# save date2 field
d = strsplit(strsplit(date, " ")[[1]][2], ".", fixed = TRUE)
mon = str_pad(d[[1]][1], 2, pad = "0")
dom = str_pad(d[[1]][2], 2, pad = "0")
date2 = paste0(2016, mon, dom)
rm(list = c("d", "mon", "dom"))
```

### Read Month Data
```{r read in sample month data, eval = FALSE}
# read in month data in opml format
month = read_xml("Data/Input/month.txt")
month = xml_children(month)[2] # get rid of head
month = xml_child(month, 1) # get XML node
```

### Read Year Data
```{r read in sample year data, eval = FALSE}
# read in year data in opml format
year = read_xml("Data/Input/year.txt")
year = xml_children(year)[2] # get rid of head
year = xml_child(year, 1) # get XML node
```

### Read 2015 Data
```{r read in 2015 data}
# read in year data in opml format
year_2015 = read_xml("Data/Input/year_2015.txt")
year_2015 = xml_children(year_2015)[2] # get rid of head
year_2015 = xml_child(year_2015, 1) # get XML node
```

### Read 2016 Data
```{r read in 2016 data}
# read in year data in opml format
year_2016 = read_xml("Data/Input/year_2016_1110.txt")
year_2016 = xml_children(year_2016)[2] # get rid of head
year_2016 = xml_child(year_2016, 1) # get XML node
```

### Set Up Days Data Frames
```{r set up days data frame}
# get all days in the year 2015 (first entry is 2015.11.17)
days_in_year_15 = as.character(seq(as.Date("2015-11-17"), as.Date("2015-12-31"), by = "days"))
days_in_year_15 = gsub(pattern = "-", replacement = "", x = days_in_year_15)
num_days_15 = length(days_in_year_15)

# set up days data frame
days_15 = tibble(
  day = days_in_year_15,
  day_of_week = rep(NA, num_days_15),
  poms_tot = rep(NA, num_days_15),
  poms_tot_w = rep(NA, num_days_15),
  poms_tot_g = rep(NA, num_days_15),
  poms_tot_h = rep(NA, num_days_15),
  poms_tot_m = rep(NA, num_days_15),
  inters_tot = rep(NA, num_days_15),
  inters_tot_p = rep(NA, num_days_15),
  inters_tot_m = rep(NA, num_days_15),
  inters_tot_s = rep(NA, num_days_15),
  inters_tot_o = rep(NA, num_days_15)
)

# get all days in the year 2016
days_in_year_16 = as.character(seq(as.Date("2016-01-01"), as.Date("2016-12-31"), by = "days"))
days_in_year_16 = gsub(pattern = "-", replacement = "", x = days_in_year_16)
num_days_16 = length(days_in_year_16)

# set up days data frame
days_16 = tibble(
  day = days_in_year_16,
  day_of_week = rep(NA, num_days_16),
  poms_tot = rep(NA, num_days_16),
  poms_tot_w = rep(NA, num_days_16),
  poms_tot_g = rep(NA, num_days_16),
  poms_tot_h = rep(NA, num_days_16),
  poms_tot_m = rep(NA, num_days_16),
  inters_tot = rep(NA, num_days_16),
  inters_tot_p = rep(NA, num_days_16),
  inters_tot_m = rep(NA, num_days_16),
  inters_tot_s = rep(NA, num_days_16),
  inters_tot_o = rep(NA, num_days_16)
)
```

### Set Up Pomodoros Data Frame
```{r set up pomodoros data frame}
pomodoros_15 = tibble(
  date = "date",
  day_of_week = "MTWTFSS",
  id = -1,
  type = "WGHM",
  proj = "ProjectName",
  proj_count = -1,
  desc = "Description"
)
pomodoros_16 = tibble(
  date = "date",
  day_of_week = "MTWTFSS",
  id = -1,
  type = "WGHM",
  proj = "ProjectName",
  proj_count = -1,
  desc = "Description"
) 
```

### Function to Get Date from Day Node
```{r get date from day node}
getDate = function(day, year) {
  # get string for date
  date = xml_attr(day, "text")
  
  # save date2 field
  d = strsplit(strsplit(date, " ")[[1]][2], ".", fixed = TRUE)
  mon = str_pad(d[[1]][1], 2, pad = "0")
  dom = str_pad(d[[1]][2], 2, pad = "0")
  date2 = paste0(year, mon, dom)
  
  return(date2)
}
```


### Function to Get Pomodoros
```{r get pomodoros for a day}
# get total pomodoros from a day
getTotPom = function(t, n) {
  t = xml_child(t, n)
  t %<>% xml_attr("text") %>% str_split(":")
  t = t[[1]][2] %>% str_trim() %>% as.integer()
  return(t)
}

getDaysPomodoros = function(day, year) {
  # get temporary days data frame
  days = get(paste0("days_", substr(year, 3, 4)))
  
  # get temporary pomodoros data frame
  pomodoros = get(paste0("pomodoros_", substr(year, 3, 4)))
  
  # get pretty date
  date = getDate(day, year)
  
  # get day of week
  day_of_week = strsplit(xml_attr(day, "text"), " ")[[1]][1]

  # get pomodoros in day
  poms = xml_children(day)[1]
  
  # pomodoros total
  poms_tot = xml_child(poms, 1)
  poms_tot_w = getTotPom(poms_tot, 1) # work
  poms_tot_g = getTotPom(poms_tot, 2) # growth
  poms_tot_h = getTotPom(poms_tot, 3) # health
  poms_tot_m = getTotPom(poms_tot, 4) # misc
  
  # if no pomodoros, can skip the rest of this
  if(!(is.na(poms_tot_w) & is.na(poms_tot_g) & is.na(poms_tot_h) & is.na(poms_tot_m))) {
    # only proceed if they're not all NAs
    # pomodoro records
    pom_records = data_frame(
      date = rep(date, 100),
      day_of_week = rep(day_of_week, 100),
      id = 1:100,
      type = rep(NA, 100),
      proj = rep(NA, 100),
      proj_count = rep(NA, 100),
      desc = rep(NA, 100)
    )
    
    # loop through each of pomodoros and log it
    for (r in 2:length(xml_children(poms))) {
      n = r - 1
      
      # get individual record
      pom_rec = xml_child(poms, r) %>%
        xml_child() %>%
        xml_attr("text") %>%
        str_split(":", 2) %>%
        .[[1]] %>%
        str_trim()
      
      # get pomodoro type
      pom_rec_type = pom_rec[1]
      
      # get pomodoro description
      pom_rec_desc = pom_rec[2]
      
      # get project type (if applicable)
      proj_check = pom_rec_desc %>%
        str_split("@") %>%
        .[[1]] %>%
        length()
      if (proj_check == 2) {
        pom_rec_proj = pom_rec_desc %>%
          str_split("@") %>%
          .[[1]] %>%
          .[2] %>%
          str_split(" ") %>%
          .[[1]] %>%
          .[1]
        
        if (grepl("\\[", pom_rec_desc)) {
          pom_rec_proj_count = pom_rec_desc %>%
            str_split("\\[", 2) %>%
            .[[1]] %>%
            .[2] %>%
            str_split("\\]", 2) %>%
            .[[1]] %>%
            .[1] %>%
            as.integer()
          
          pom_rec_desc %<>%
            str_split("]") %>%
            .[[1]] %>%
            .[2] %>%
            str_trim()
        } else {
          pom_rec_proj_count = NA
        }
        
        proj_bool = pom_rec_desc %>%
          str_split(" ") %>%
          .[[1]] %>%
          grepl("@", .)
        pom_rec_desc %<>%
          str_split(" ") %>%
          .[[1]] %>%
          subset(!proj_bool) %>%
          paste(collapse = " ")
        
      } else {
        pom_rec_proj = NA
        pom_rec_proj_count = NA
      }
      
      # add results to pom_records
      pom_records$type[n] = pom_rec_type
      pom_records$proj[n] = pom_rec_proj
      pom_records$proj_count[n] = pom_rec_proj_count
      pom_records$desc[n] = pom_rec_desc
    }
    
    # filter out extra rows
    pom_records %<>% filter(!is.na(type))
    
    # add to pomodoros data frame
    pomodoros %<>% rbind(pom_records)
    
    # add totals to days data frame
    days$poms_tot[days$day == date] = nrow(pom_records)
    days$poms_tot_w[days$day == date] = pom_records %>% filter(type == "W") %>% nrow()
    days$poms_tot_g[days$day == date] = pom_records %>% filter(type == "G") %>% nrow()
    days$poms_tot_h[days$day == date] = pom_records %>% filter(type == "H") %>% nrow()
    days$poms_tot_m[days$day == date] = pom_records %>% filter(type == "M") %>% nrow()
  }

  # add day of week
  days$day_of_week[days$day == date] = day_of_week
  
  # save results to global environment
  assign(paste0("days_", substr(year, 3, 4)), days, envir = .GlobalEnv)
  assign(paste0("pomodoros_", substr(year, 3, 4)), pomodoros, envir = .GlobalEnv)
  
}
```

### Function to Get Interruptions
```{r get interruptions in a day}
# get total interruptions for a day
getTotInter = function(t, n) {
  t = xml_child(t, n)
  t %<>% xml_attr("text") %>% str_split(":")
  t = t[[1]][2] %>% str_trim() %>% as.integer()
  return(t)
}

getDaysInterruptions = function(day, year) {
  # get temporary days data frame
  days = get(paste0("days_", substr(year, 3, 4)))
  
  # get pretty date
  date = getDate(day, year)
  
  # get interruptions in a day
  inters = xml_children(day)[2]
  
  ## interruptions total
  inters_tot_p = getTotInter(inters, 1) # peer
  inters_tot_m = getTotInter(inters, 2) # manager
  inters_tot_s = getTotInter(inters, 3) # self
  inters_tot_o = getTotInter(inters, 4) # other
  inters_tot = sum(inters_tot_p, inters_tot_m, inters_tot_s, inters_tot_o, na.rm = T)
  
  # if no interruptions, can skip the rest of this
  if (!(is.na(inters_tot_p) & is.na(inters_tot_m) & is.na(inters_tot_s) & is.na(inters_tot_o))) {
    # only proceed if they're not all NA
    
    # add totals to days data frame
    days$inters_tot[days$day == date] = inters_tot
    days$inters_tot_p[days$day == date] = inters_tot_p
    days$inters_tot_m[days$day == date] = inters_tot_m
    days$inters_tot_s[days$day == date] = inters_tot_s
    days$inters_tot_o[days$day == date] = inters_tot_o
    
    # save result to global environment
    assign(paste0("days_", substr(year, 3, 4)), days, envir = .GlobalEnv)
  }

}
```

## Parse Data
### Get Results for a Single Day
```{r test results for a single day, eval = FALSE}
# getDaysPomodoros(day)
# getDaysInterruptions(day)
```


### Get Results for a Single Month
```{r function to get results for a single month}
getMonthResults = function(month, year) {
  for (day in xml_children(month)) {
    getDaysPomodoros(day, year)
    getDaysInterruptions(day, year)
  }
}
```

### Get Results for a Single Year
```{r function to get results for a single year}
getYearResults = function(year, year_txt) {
  for (month in xml_children(year)) {
    getMonthResults(month, year_txt)
  }
}
```

### Get Results for 2015
```{r get 2015 results}
getYearResults(year_2015, "2015")
```

### Get Results for 2016
```{r get 2016 results}
getYearResults(year_2016, "2016")
```

## Save Output
```{r save csv output files}
write_csv(days_15, "Data/Output/days_15.csv")
write_csv(pomodoros_15, "Data/Output/pomodoros_15.csv")
write_csv(days_16, "Data/Output/days_16.csv")
write_csv(pomodoros_16, "Data/Output/pomodoros_16.csv")
```

